Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-06-27 edubots_surveys.Rnw
Fixing small typo
More meta-reviews

\begin{abstract} % abstract
Introducing new technologies such as messaging platforms, and chatbots
attached to it, in higher education, requires careful consideration of
all options, but above all, an examination of the attitudes of the
affected community, especially those that will need to handle them,
% Antonio - I would say 'to manage them'. Students should also handle new technologies. ;)
teachers.
In this paper we have surveyed the opinions of tertiary education
teachers based mainly in Spain and Spanish speaking countries, 
% Antonio - Spanish-speaking?
looking at what they think about the introduction 
% Antonio - inthe classroom
of messaging platforms and chatbots, what their needs are, what kind of use cases they see for
them, and in what kind of environment they think its use will be
valuable. We will examine how and when these attitudes vary across
gender, experience, and other factors, such as the type of discipline
they are teaching. Our conclusions might help with the adoption of
messaging platforms in an educational setting, as well as chatbots or
other kind of bots, by higher education institution, and how these
must be introduced to teachers so that it helps them achieve desired
educational outcomes. 
\end{abstract}

@@

Nevertheless, there are challenges when using MIM tools that occur due
to the blurring of boundaries between academic and private life. This
can lead to technostress \cite{gachago2015crossing}, difficulty in
managing responsibilities, especially among mature students, and lack of
privacy \cite{tang2017mobile}.  Students' dropout of the MIM groups,
as they can leave groups at any time, can hinder their learning and
undermine educators' efforts \cite{mwakapina2016whatsapp}.  In
addition, there is a need to set rules and norms for these MIM groups
in order to maintain the safety of these online communities for
students \cite{abbas2021onlinechat}. However, these rules should not affect students'
ownership and control, since it is vital to advance in their learning
\cite{gachago2015crossing} precess. 
This is why examining the role of MIM in higher education is still a challenge, and why the attitudes of the teaching community towards them have to be examined, as we do in this paper.

@@

Several higher education chatbots' evaluation studies have been 
undertaken. For instance, a recent evaluation review study presented by Smutny and Schreiberova 
\cite{Smutny2020} examined 47 educational chatbots implemented in
Facebook Messenger with the focus to identify characteristics and
quality metrics such as language, subject matter and platform. Another
study aimed to categorise educational chatbots according to their
purpose into service-oriented and teaching-oriented
\cite{perez2020rediscovering}. The first category includes those that
provide service support such as the chatbot Ask Holly \cite{meetholly}
and Dina \cite{santoso2018dinus}; both chatbots respond to students'
questions about enrollment and registration. Ask (Lancaster University)
 \cite{LancasterUniversity_2019} answers students' frequently
asked questions about timetables, grades, tutors and societies. LISA
\cite{dibitonto2018chatbot} and Differ \cite{differ.chat} facilitate
breaking the ice between new students by introducing them to each
other. Ranoliya et al. \cite{ranoliya2017chatbot} proposed a generic chatbot for
university students that is able to answer to their frequently asked
questions. 
For some time, the University of Granada had ELVIRA as a
chatbot in its main web page \cite{MOREO20129}. Besides being able to
answer pre-established (frequent) questions, it did so from the website of the
University of Granada using an inset character, voiced by a real
person, who lip-synched the answers. The emphasis in this case,
however, was on the authenticity of the synchronization more than in
making the update of questions and answers simpler, or more
interactive, using actual messaging platforms. 
% Antonio - the last part of the sentence is not clear. Do you refer to all the aforementioned chatbots?
% Just to Elvira? What messaging platforms do you mean?
In most cases, using the inset search engine was able to give you more up-to-date and
accurate answers.
% Antonio - again, are you speaking about Elvira? 
% If we say something like the last sentence, we are actually saying that chatbots are not useful... is this what we want to remark?

On the other hand, teaching-oriented chatbots are more sophisticated,
as they set personalised learning outcomes and monitor learning
progress. For instance, the work \cite{fernoagua2018intelligent} reported on
''eduAssistant'', a virtual teaching assistant chatbot developed inside the
Telegram messaging platform. In this study, Telegram platform was
chosen because it is easy to use, students are familiar with its
features, and it enables users to exchange messages in different
formats (text, audio and video) \cite{fernoagua2018intelligent}. In
addition, Telegram run on all devices and operating
systems. ''eduAssistant'' chatbot acts as an automatic agent
in teacher-content-student, facilitating real-time feedback
loops and providing a personalised learning experience relevant to the
students' acquired skills and knowledge. Using this chatbot, educators can
create interactive instances in their lectures where they pose
questions to their students and the chatbot assists those who need
further help by giving them more hints and reporting it to their
educator's dashboard \cite{fernoagua2018intelligent}. This can help 
educators to locate those students that need their attention and send to 
them more educational resources relevant to their academic attainment.

Despite its (arguably) successful implementation in different higher education institutions, 
over all in the fringes of educational activity, its implementation or deployment is not trivial.
Authors in \cite{sjostrom2018designing} have proposed a conceptual
architecture for the adoption of teaching-oriented chatbots in higher education.  This
conceptual architecture is based on a systematic literature review of
previous studies, examining the design of chatbots in higher education, as well as a content 
analysis of student emails and discussion forum posts of
four instances of a Java programming course.  The study outlined
several design considerations; among them, the authors emphasised the
importance of developing chatbots in platforms that students and
educators are familiar with and can easily access (i.e. Facebook
Messenger) which was confirmed with \cite{hobert2019you} and
\cite{fernoagua2018intelligent} studies. In addition, Sj{\"o}str{\"o}m et al. \cite{sjostrom2018designing} 
argued that a conceptualision of learners' questions could aid designers in integrating the appropriate
types of questions that the chatbots should support for different
courses.  Coronado et al. \cite{coronado2018cognitive} proposed agents that store
learning materials to be provided on demand to students, whereas the authors in
\cite{crockett2017predicting} reported on tutoring systems,
which can perform initial assessments of students' understanding and
provide learning material that would advance their understanding to
the next level.

@@

In this line, our previous work \cite{MoraChatbots2021} aimed at analysing the expectations of students on this regard, whereas the present study is focused on the other key actor in this challenge, i.e. educators.

>>>>

\begin{abstract} % abstract
Introducing new technologies such as messaging platforms, and chatbots
attached to it, in higher education, requires careful consideration of
all options, but above all, an examination of the attitudes of the
affected community, especially those that will need to handle them,
% Antonio - I would say 'to manage them'. Students should also handle new technologies. ;)
% We're talking about teachers here, who need to handle the outcomes and introduce them in class - JJ
teachers.
In this paper we have surveyed the opinions of tertiary education
teachers based mainly in Spain and Spanish-speaking countries, 
looking at what they think about the introduction 
% Antonio - inthe classroom
% that's implied - JJ
of messaging platforms and chatbots, what their needs are, what kind of use cases they see for
them, and in what kind of environment they think its use will be
valuable. We will examine how and when these attitudes vary across
gender, experience, and other factors, such as the broad discipline
they are teaching. Our conclusions might help with the adoption of
messaging platforms in an educational setting, as well as chatbots or
other kind of bots, by higher education institution, and how these
must be introduced to teachers so that it helps them achieve desired
educational outcomes. 
\end{abstract}

@@

Nevertheless, there are challenges when using MIM tools that occur due
to the blurring of boundaries between academic and private life. This
can lead to technostress \cite{gachago2015crossing}, difficulty in
managing responsibilities, especially among mature students, and lack of
privacy \cite{tang2017mobile}.  Students' dropout of the MIM groups,
as they can leave groups at any time, can hinder their learning and
undermine educators' efforts \cite{mwakapina2016whatsapp}.  In
addition, there is a need to set rules and norms for these MIM groups
in order to maintain the safety of these online communities for
students \cite{abbas2021onlinechat}. However, these rules should not affect students'
ownership and control, since it is vital to advance in their learning
\cite{gachago2015crossing} process. 
This is why examining the role of MIM in higher education is still a challenge, and why the attitudes of the teaching community towards them have to be examined, as we do in this paper.

@@

Several higher education chatbots' evaluation studies have been 
undertaken. For instance, a recent evaluation review study presented by Smutny and Schreiberova 
\cite{Smutny2020} examined 47 educational chatbots implemented in
Facebook Messenger with the focus to identify characteristics and
quality metrics such as language, subject matter and platform. Another
study aimed to categorise educational chatbots according to their
purpose into service-oriented and teaching-oriented
\cite{perez2020rediscovering}. The first category includes those that
provide service support such as the chatbot Ask Holly \cite{meetholly}
and Dina \cite{santoso2018dinus}; both chatbots respond to students'
questions about enrollment and registration. Ask L. U.
 \cite{LancasterUniversity_2019} answers students' frequently
asked questions about timetables, grades, tutors and societies. LISA
\cite{dibitonto2018chatbot} and Differ \cite{differ.chat} facilitate
breaking the ice between new students by introducing them to each
other. Ranoliya et al. \cite{ranoliya2017chatbot} proposed a generic chatbot for
university students that is able to answer to their frequently asked
questions. 
For some time, the University of Granada had ELVIRA as a
chatbot in its main web page \cite{MOREO20129}. Besides being able to
answer pre-established (frequent) questions, it did so from the website of the
University of Granada using an inset character, voiced by a real
person, who lip-synched the answers. The emphasis in the case of Elvira,
however, was on the authenticity of the synchronization more than in
making the update of questions and answers simpler, or more
interactive, using actual messaging platforms. 
% Antonio - the last part of the sentence is not clear. Do you refer to all the aforementioned chatbots?
% Just to Elvira? What messaging platforms do you mean?
% Only Elvira - JJ
In most cases, using the inset search engine was able to give you more up-to-date and
accurate answers than the ones provided by ELVIRA, which had to be updated by hand (and not too often).
% Antonio - again, are you speaking about Elvira? 
% If we say something like the last sentence, we are actually saying that chatbots are not useful... is this what we want to remark?
% No, we're saying that chatbots like Elvira have limited usability, unlike chatbots in messaging platforms - JJ

On the other hand, teaching-oriented chatbots are more sophisticated,
as they set personalised learning outcomes and monitor learning
progress. For instance, \cite{fernoagua2018intelligent} reported on
''eduAssistant'', a virtual teaching assistant chatbot developed on the
Telegram messaging platform. In this study, Telegram platform was
chosen because it is easy to use, students are familiar with its
features, and it enables them to exchange messages in different
formats (text, audio and video) \cite{fernoagua2018intelligent}. In
addition, Telegram could operate on all devices and operating
systems. The ''eduAssistant'' chatbot acts as an automatic agent
in teacher-content-student, facilitating real-time feedback
loops and providing a personalised learning experience relevant to the
students' acquired skills and knowledge. Using this chatbot, educators can
create interactive instances in their lectures where they pose
questions to their students and the chatbot assists those who need
further help by giving them more hints and reporting it to their
educator's dashboard \cite{fernoagua2018intelligent}. This can help 
educators to locate those students that need their attention and send to 
them more educational resources relevant to their academic attainment.

Despite its (arguably) successful implementation in different higher education institutions, 
over all in the fringes of educational activity, its implementation or deployment is not trivial.
Some authors, for instance \cite{sjostrom2018designing} have proposed a conceptual
architecture for the adoption of teaching-oriented chatbots in higher education.  This
conceptual architecture is based on a systematic literature review of
previous studies, examining the design of chatbots in higher education, as well as making a content 
analysis of student emails and discussion forum posts of
four instances of a Java programming course.  The study outlined
several design considerations; among them, the authors emphasised the
importance of developing chatbots in platforms that students and
educators are familiar with and can easily access (i.e. Facebook
Messenger) which was confirmed with \cite{hobert2019you} and
\cite{fernoagua2018intelligent} studies. In addition, Sj{\"o}str{\"o}m et al. \cite{sjostrom2018designing} 
argued that a conceptualision of learners' questions could aid designers in integrating the appropriate
types of questions that the chatbots should support for different
courses.  Coronado et al. \cite{coronado2018cognitive} proposed agents that store
learning materials to be provided on demand to students, whereas the authors in
\cite{crockett2017predicting} reported on tutoring systems,
which can perform initial assessments of students' understanding and
provide learning material that would advance their understanding to
the next level.

@@

Along this line of work, our previous work \cite{MoraChatbots2021} aimed at analysing the expectations of students on this regard, whereas the present study is focused on the other key actor in this challenge, i.e. educators.
